### 2020-09-05 latex/vlp.tex
Added the images for vlp controllers, except the smooth one

\begin{figure}
   \centering
   \includestandalone[width=0.5\textwidth]{images/vlp_optimal_controller_qp_plane}
   \caption{The representation of the time-optimal controller for a standing
      swing in the \((q,p)\)-plane. As per 
      \cite{pumping_swing_standing_squatting}, the red region corresponds to
      squatting and the blue region corresponds to standing.}
      \label{fig:vlp-optimal-controller-qp-plane}
\end{figure}

\begin{figure}
   \centering
   \includestandalone[width=0.5\textwidth]{images/vlp_optimal_controller}
   \caption{The time-optimal VLP controller converted to a discontinuous
   function \(l(\theta)\), where \(\theta := \arctan_2(p,q)\).}\label{fig:vlp-optimal-controller}
\end{figure}

To find a continuously differentiable function which approximates this controller,
we can attach sinusoids at the transition points of
\(l^\star(\theta)\) (see Figure \ref{fig:vlp-T-controller}). Let
\(\Delta l := (\overline{l} - \underline{l})/2\) and 
\(l_{\text{avg}} := (\overline{l} + \underline{l})/2\).
Providing these newly attached sinusoids with a frequency \(\omega = \frac{pi}{T}\) 
(where \(T \in ]0,\frac{\pi}{2}]\) is a control parameter), we have a new
controller \(l_T(\theta)\):
\begin{equation}\label{eqn:vlp-T-controller}
   l_T(\theta) = \begin{cases}
      \underline{l} & \theta \in \left[-\pi + \frac{T}{2}, -\frac{\pi}{2} - \frac{T}{2}\right] 
      \cup \left[\frac{T}{2}, \frac{\pi}{2} - \frac{T}{2}\right] \\
      \overline{l} & \theta \in \left[-\frac{\pi}{2} + \frac{T}{2}, -\frac{T}{2}\right] 
      \cup \left[\frac{\pi}{2} + \frac{T}{2}, \pi - \frac{T}{2}\right] \\
      -\Delta l \sin(\omega(\theta + \pi)) + l_{\text{avg}} & \theta \in
      \left[-\pi,-\pi + \frac{T}{2}\right] \\
      -\Delta l \sin(\omega(\theta - a)) + l_\text{avg} & 
      \theta \in \left[a - \frac{T}{2}, a + \frac{T}{2}\right] \text{ for } 
      a \in \left\{-\frac{\pi}{2}, 0, \frac{\pi}{2}\right\} \\
      -\Delta l \sin(\omega(\theta-\pi)) & \theta \in \left[\pi - \frac{T}{2},\pi\right] \\
   \end{cases}
\end{equation}

\begin{figure}
   \centering
   % TODO: Insert an image of the controller with sinusoids attached
   \caption{}\label{fig:vlp-T-controller}
\end{figure}

>>>>

\begin{figure}
   \centering
   \begin{subfigure}[t]{0.45\textwidth}
      \includestandalone[width=\linewidth]{images/vlp_optimal_controller_qp_plane}
      \caption{The time-optimal controller mapped to the \((q,p)\)-plane.}
      \label{fig:vlp-optimal-controller-qp-plane}
   \end{subfigure}
   \hfill
   \begin{subfigure}[t]{0.45\textwidth}
      \includestandalone[width=\linewidth]{images/vlp_optimal_controller}
      \caption{The time-optimal controller converted to a VNHC-style 
      function \(l^\star(\theta)\), where \(\theta := \arctan_2(p,q)\).}\label{fig:vlp-optimal-controller}
   \end{subfigure}
   \caption{The time-optimal controller for a standing swing as derived by
      \cite{pumping_swing_standing_squatting}. The colour red
      corresponds to standing and blue to squatting.}
\end{figure}

To find a continuously differentiable function which approximates this controller,
we can attach sinusoids at the transition points of
\(l^\star(\theta)\) (see Figure \ref{fig:vlp-T-controller}). Let
\(\Delta l := (\overline{l} - \underline{l})/2\) and 
\(l_{\text{avg}} := (\overline{l} + \underline{l})/2\).
Providing these newly attached sinusoids with a frequency \(\omega = \frac{pi}{T}\) 
(where \(T \in ]0,\frac{\pi}{2}]\) is a control parameter), we have a new
controller \(l_T(\theta)\):
\begin{equation}\label{eqn:vlp-T-controller}
   l_T(\theta) = \begin{cases}
      \underline{l} & \theta \in \left[-\pi + \frac{T}{2}, -\frac{\pi}{2} - \frac{T}{2}\right] 
      \cup \left[\frac{T}{2}, \frac{\pi}{2} - \frac{T}{2}\right] \\
      \overline{l} & \theta \in \left[-\frac{\pi}{2} + \frac{T}{2}, -\frac{T}{2}\right] 
      \cup \left[\frac{\pi}{2} + \frac{T}{2}, \pi - \frac{T}{2}\right] \\
      -\Delta l \sin(\omega(\theta + \pi)) + l_{\text{avg}} & \theta \in
      \left[-\pi,-\pi + \frac{T}{2}\right] \\
      -\Delta l \sin(\omega \theta) + l_\text{avg} & \theta \in [-\frac{T}{2},
      \frac{T}{2}] \\
      \Delta l \sin(\omega(\theta - a)) + l_\text{avg} & 
      \theta \in \left[a - \frac{T}{2}, a + \frac{T}{2}\right] \text{ for } 
      a \in \left\{-\frac{\pi}{2}, \frac{\pi}{2}\right\} \\
      -\Delta l \sin(\omega(\theta-\pi)) & \theta \in \left[\pi - \frac{T}{2},\pi\right] \\
   \end{cases}
\end{equation}

\begin{figure}
   \centering
   \includestandalone[width=0.6\textwidth]{images/vlp_T_controller}
   \caption{The continuous VNHC-style VLP controller \(l_T(\theta)\).}\label{fig:vlp-T-controller}
\end{figure}
